On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-06-17 documents/paper.tex
Teensy

Additionally, other mechanisms may produce superior results and should be evaluated in the same context. Recent data on far UVC [Buonanno 2017] indicate safety.

@@

The medium (not specified in the paper, but ATCC recommends that MDCK cells are grown in Eagle's MEM + 10\% fetal bovine serum).

[IEEE C95.1-2019]

[IEEE C95.1-2005]

@@

On the other hand, a personal device may present issues with compliance\footnote{that sounds evil, but it really isn't} and production volume.

@@

\noindent\fbox{\parbox{\linewidth}{
	Toolchain:
	\begin{itemize}
	\item QUCS 0.0.20 for AC simulation, with python-qucs and scipy's 'basinhopper' for optimization
	\item gprMax for FDTD EM simulation
	\item KiCAD, wcalc, scikit-rf, ngspice
	\end{itemize}
}}
%
The following properties: P1dB

@@

However, with this PCB substrate, a loss of only 0.026 dB/mm on signals of minimum 0 dBm. We are also only minimally concerned with $S_{11}$ reflections, noise, or spurs (viruses do not have a discriminating palate), so precise impedance control is not required; the wideband VCO sweep accomodates for any variations in resonant frequency due to wide manufacturing tolerances.

@@

The key sticking point - which we missed - seems to be that at these scales, using microstrip design techniques, the parasitics of any possible filter structure are so large that the small change in inductance that varactors can provide cannot tune the circuit by any meaningful amount.

@@

@@

@@

\end{itemize}\
%
However, a third element is also required:
%
\begin{itemize}
\item A frequency-selective element that restricts oscillation modes and decreases phase noise.
\end{itemize}
%
Without this element, proximity effects from nearby flesh, startup instablity, mode-hopping, and de-tuning were all encountered.

@@

@@

Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck. Any comparable dimwit to the author would have accomplished the same under the same conditions.

It is infinitely to be regretted that such equally capable people were stuck in warehouses doing menial 15-hour shifts or assembling smartphones.

Chiefly among the enablers are of course my parents, Doris and Brian, without which this work would have been done by someone else[] - but who also supported this work financially. Brian

@@

The only reference to a 3 - 96 GHz limit we can find is that of Section 4.6, {\it Relaxation of the power density MPEs for localized exposures}, where the equation is $200 (f/3)^{1/5} \text{ W/m}^2$ [IEEE C95.1-2005]; but this is for controlled, occupational exposures only, referring to Table 8. For Table 9, general public, the equation is $18.56 (f)^{0.699} \text{ W/m}^2$, or $64.93 \text{ W}/\text{m}^2$ @ 6 GHz.

We don't think this changes the substance of [Yang 2015]'s paper, if it is an error; the relaxed localized exposure is probably the correct threshold to use, and it just means the mechanism is more useful for healthcare workers who acknowledge the risks.

@@

@@

Again, inductive choke biasing in the feedback loop was practically impossible. Biasing PiN diodes with a 10kohm resistor, (with 330 ohm safety resistor) one to 48V bias and another through an N-channel mosfet worked fine. The oscillator ran fine with a PiN bias of 2.34 mA. [LO prototype N]. Such a high bias voltage was required to get sufficient current through the PiN while remaining delicate with the vfb.

@@

>>>>

Additionally, other sterilization techniques may produce superior results and should be evaluated in the same context. Data on far UVC [Buonanno 2017] indicate safety.

@@

@@

On the other hand, a personal device may present issues with participation and production volume.

@@

\noindent\fbox{\parbox{\linewidth}{
	Toolchain:
	\begin{itemize}
	\item Failed oscillator feedback-loop optimization toolchain: QUCS 0.0.20 + python-qucs + scipy's 'basinhopper'
	\item Successful A slightly modified ngspice + ngspyce + pyEVTK
	\item gprMax for FDTD EM simulation
	\item KiCAD, wcalc, scikit-rf, ngspice
	\end{itemize}
}}
%

The oscillator is a 'wideband double-tuned varactor VCO', based almost verbatim on [Tsuru 2008] and the reference design in Figure 8.36, p378 of [Grebennikov 2007].

The rest of the papers in the bibliography were highly enlightening regarding the principles of microwave oscillator design.

This topology of oscillator worked marvellously on essentially the first try.

The process by which we failed miserably to design our own oscillator topology is detailed in the supplemental.

The following properties: P1dB

@@

However, with this PCB substrate, the expected loss of only 0.026 dB/mm on signals of minimum 0 dBm is patently acceptable. As viruses do not have a discriminating palate, we are also only minimally concerned with $S_{11}$ reflections, noise, or spurs, so precise impedance control is not required; the wideband VCO sweep accomodates for any variations in resonant frequency due to wide manufacturing tolerances.

@@

The key sticking point - which we missed - seems to be that at these scales, using microstrip design techniques, the parasitics of any possible filter structure are so large that the small change in impedance that varactors can provide cannot tune the circuit by any meaningful amount.

@@

Optimizing S-parameter simulations of the feedback loop and negative-resistance device did not produce an accurate picture of the oscillator. While the phase and frequency response appeared to be excellent, the transient response painted a different picture:

[gnuplot transient sim here]

The complete transient simulation matched reality very closely.

@@

This is apparently known as a "double-tuned" wideband.

@@

\end{itemize}\
%
However, a third element is also required:
%
\begin{itemize}
\item A frequency-selective element that restricts oscillation modes and decreases phase noise.
\end{itemize}
%

With large feedback-loop structures, such as PiN switched lines, proximity effects from nearby flesh would detune the oscillator to a s

@@

\paragraph{\textbf{Spacing}}\

FDTD results still yielded some coupling at 2 mm isolation.

\paragraph{\textbf{Via stitching}}\

Rather than the almost universal technique of via stitching components immediately to the ground plane (a tedious process with our prototyping setup), a large ground pour on the component layer was used, similar to [Hunter? combline]. Since we use microstrip rather than coplanar waveguide,

Since the ground plane does not participate in the DC bias at all, no vias are required in the final device. This means that the comparatively slow drilling, electroless strike and electroplating steps are unneccesary for this device.

@@

Special thanks to all the people - most equally capable of writing this paper if provided the opportunity - who work menial shifts at the component suppliers that remained open that were so critical. Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.

Chiefly among the enablers are of course my parents, Doris and Brian, without whom this work would have been done by someone else, and who also supported this work financially.

@@

The only reference to a 3 - 96 GHz limit we can find is that of Section 4.6, {\it Relaxation of the power density MPEs for localized exposures}, where the equation is $200 (f/3)^{1/5} \text{ W/m}^2$ [IEEE C95.1-2005], for controlled occupational exposures, referring to Table 8. For Table 9, general public, the equation is $18.56 (f)^{0.699} \text{ W/m}^2$, or $64.93 \text{ W}/\text{m}^2$ @ 6 GHz.

@@

In any case, this doesn't change the substance of [Yang 2015]'s paper; the relaxed localized exposure is probably the correct threshold to use, and it just means the mechanism is more useful for healthcare workers who acknowledge the risks.

@@

Again, inductive choke biasing in the feedback loop was practically impossible. Biasing PiN diodes with a 10kohm resistor, (with 330 ohm safety resistor) one to 48V bias and another through an 2N7002P N-channel mosfet worked fine.

The oscillator ran fine with a PiN bias of 2.34 mA. [LO prototype N]. A high bias voltage of 48V was required to get sufficient current through the two 10K resistors and the PiN diode to obtain a low impedance while remaining delicate with the vfb.

The PiN diode used has a resting resistance of 500 ohms, 5 ohms at 2 mA and 2 ohms at ??.

48V is a little tight on the 50V rated voltage of our DC blocking capacitors.

Each activated PiN diode should be biased separately, since putting 2x 2 mA through 20K would take an impractical 80V.

@@

It is far easier to use existing, well-characterized reference designs verbatim than to modify
